A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-12 docs/methods/erosion_methods.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion}. Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, domokos2014river}. Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
